Gaze-dependent evidence accumulation predicts multi-alternative risky choice behaviour

### 2021-02-05 manuscript/main.tex
added author contributions, acknowledgments, fixed affiliations

\author[1,2,*]{\small Felix Molter}
\author[3]{\small Armin W. Thomas}
\author[4,5]{\small Scott A. Huettel}
\author[2]{\small Hauke R. Heekeren}
\author[1,2]{\small Peter N. C. Mohr}
\affil[1]{\footnotesize School of Business \& Economics, Freie Universität Berlin, Berlin, Germany}
\affil[2]{\footnotesize Center for Cognitive Neuroscience, Freie Universität Berlin, Berlin, Germany}
\affil[3]{\footnotesize Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany}
\affil[4]{\footnotesize Center for Cognitive Neuroscience, Duke University, Durham, NC, USA}
\affil[5]{\footnotesize Department for Psychology and Neuroscience, Duke University, Durham, NC, USA}
\affil[*]{\footnotesize E-mail: \href{mailto:felixmolter@gmail.com}{felixmolter@gmail.com}}

@@

\section*{Author contributions}
F.M., P.N.C.M. and S.A.H. designed the study. F.M. and A.W.T. conceptualized the behavioural models. F.M. performed the experiment, wrote all software, analysed the data and visualized results. P.N.C.M. and H.R.H. supervised the project. F.M. wrote the original draft. All authors reviewed and edited the manuscript.

>>>>

\author[1,2,*]{\small Felix Molter}
\author[2,3,4]{\small Armin W. Thomas}
\author[5,6]{\small Scott A. Huettel}
\author[2]{\small Hauke R. Heekeren}
\author[1,2]{\small Peter N. C. Mohr}
\affil[1]{\footnotesize School of Business \& Economics, Freie Universität Berlin, Berlin, Germany}
\affil[2]{\footnotesize Center for Cognitive Neuroscience, Freie Universität Berlin, Berlin, Germany}
\affil[3]{\footnotesize Stanford Data Science, Stanford University, Stanford, CA, USA}
\affil[4]{\footnotesize Department of Psychology, Stanford University, Stanford, CA, USA}
\affil[5]{\footnotesize Center for Cognitive Neuroscience, Duke University, Durham, NC, USA}
\affil[6]{\footnotesize Department for Psychology and Neuroscience, Duke University, Durham, NC, USA}
\affil[*]{\footnotesize E-mail: \href{mailto:felixmolter@gmail.com}{felixmolter@gmail.com}}

@@

\section*{Author contributions}
F.M., S.A.H. and P.N.C.M. designed the study. F.M. and A.W.T. conceptualized the behavioural models. F.M. performed the experiment, wrote all software, analysed the data and visualized results. P.N.C.M. and H.R.H. supervised the project. F.M. wrote the original draft. All authors reviewed and edited the manuscript.
